Southampton: Mapping Energy Poverty & Deprivation

### 2021-07-26 mappingSotonEnergyDeprivation.Rmd
added colour fill by variable to leaflet map h/t @twrushby

Figure \@ref(fig:mapLeaflet) shows a leaflet version for pretty background to identify locations

```{r mapLeaflet, fig.cap="Location of filtered LSOAs"}
# https://dataknut.github.io/mapping-with-r/ONS-open-geography.html
library(leaflet)

@@

leaflet(map_df_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = "blue", fillColor = "blue", fillOpacity = 0.2, weight = 1.5, popup = ~(LSOA11CD), # popups clicked
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

>>>>

Figure \@ref(fig:mapLeaflet) shows a leaflet version for pretty background to identify locations. When selected the LSOAs are coloured by their IMD Score.

```{r mapLeaflet, fig.cap="Location of filtered LSOAs (coloured by IMD score)"}
# https://dataknut.github.io/mapping-with-r/ONS-open-geography.html
library(leaflet)

@@

#h/t @tom_rushby - see also https://rstudio.github.io/leaflet/colors.html

qpal <- colorNumeric("Reds", map_df_trans$IMDScore, n = 9)

leaflet(map_df_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = ~qpal(IMDScore),
              fillOpacity = 0.2, weight = 1.5, popup = ~(LSOA11CD), # popups clicked
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))
